Building a continuous benchmarking ecosystem in bioinformatics

### 2025-07-17 2_second_review/manuscript_with_tracked_changes.tex
first round completed

@@

@@

Benchmarking systems are software meant to orchestrate other software (e.g. benchmarked methods). Software are run on specific hardware, from commodity computers to dedicated hardware, often large servers or academic and commercial clouds, posing a challenge: benchmarked methods should have access to comparable resources (hardware).

compilation flags

multiarch, ARMs

containers, discuss software then

computing quotas, concurrency, IO

how to profile performance and fingerprint resources
}

>>>>

{\color{red} Transparency and clear governance guidelines provide an effective to detect and react to potential misuse, e.g. by explicit rules to validate results. Other ethical considerations include facilitating safe interactions and fair resources allocation and efficiency. Clear code of conduct statements proactively flagging harassment (e.g., by sex, ethnicity or academic seniority, among others) provide explicit means to ease collaboration. In terms of efficiency, comparable resources allocation (e.g., computing power, support) to all contribuors, while also being aware of $CO_2$ emissions, could also be spelled out in the governance model.}

@@

Software, both from benchmarking systems or from the benchmarking workflow and hence benchmarked methods, can be run in different hardware, from commodity computers to dedicated hardware, often large servers or academic and commercial clouds. Performance profiling (e.g., how fast a benchmarked method runs) requires access to fair and comparable resources.

Comparable resources can be provisioned on demand in cloud computing, or can be ensured by deploying benchmarking systems in controlled and dedicated hardware. Ideally, performance results (e.g., wallclock time) could be bundled to metadata describing the used hardware (e.g., CPU characteristics).

It is worth noting that CPU microarchitecture influences performance, particularly when using optimized compilers to improve performance of benchmarked methods at the expense of making binaries microarchitecture-specific. This feature is not solved by containerization. Benchmarking systems can automate software installations with equivalent degrees of optimization across benchmarked methods, and/or provide multiarchitecture builds.

Finally, benchmarking methods could benefit from the high performance computing-style user quotas and timeouts to cap the maximum memory and/or CPU cycles each method can use.}

@@
